Frequent Payment \thanks{}

### 2019-08-30 main.tex
run do files
worked on take up, and on the TE dofile

\begin{figure}[H]
        \caption{Timeline of the experiment}
    \label{micas}
    \begin{center}
        \centering
        \includegraphics[width=0.70\textwidth]{Figuras/timeline_suc_exp.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{timeline\_suc\_exp.do}}
\end{figure}

\begin{figure}[H]
        \caption{Experiment arms}
    \label{micas}
    \begin{center}
        \centering
        \includegraphics[width=0.70\textwidth]{Figuras/exp_arms.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ }
\end{figure}

@@

\begin{figure}[H]
    \caption{Treatment Effect}
    \label{Treatment Effect}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Paid loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_des_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_num_p.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Percentage of payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_sum_porcp_c.pdf}
    \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
      \caption{Days to un-pledge}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_dias_al_desempenyo.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
\end{figure}

\begin{figure}[H]
        \caption{Reincidence}
    \label{micas}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_reincidence.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ }
\end{figure}

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect}
    \label{Treatment Effect}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Paid loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_num_p.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Percentage of payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_sum_porcp_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
      \caption{Days to un-pledge}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_dias_al_desempenyo.pdf}
    \end{subfigure}    
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf.do}}
\end{figure}

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect for Paid Loan Branches}
    \label{Treatment Effect branch}
    \begin{center}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_3.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_3.pdf}
    \end{subfigure}
     \begin{subfigure}{0.3\textwidth}
      \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
      \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_dist_des_c_pro_5.pdf}
    \end{subfigure} 
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_5.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf.do}}
\end{figure}

@@

@@

\begin{figure}[H]
    \caption{Robustness check effect of arms in reincidence}
    \label{Evolution payment}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
        \caption{ No Choice/Fee}
        \centering
        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p2.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
      \caption*{No Choice/No fee}
        \centering
        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p3.pdf}
    \end{subfigure}

@@

\begin{figure}[H]
    \caption{Treatment Effect (conditional to positive payment)}
    \label{Treatment Effect}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Paid loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_des_c_robust.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_num_p_robust.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Percentage of payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_sum_porcp_c_robust.pdf}
    \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
      \caption{Days to un-pledge}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_dias_al_desempenyo_robust.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
\end{figure}

\begin{figure}[H]
        \caption{Reincidence (conditional to positive payment)}
    \label{micas}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_reincidence_robust.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ }
\end{figure}

>>>>

\begin{figure}[H]
        \caption{Timeline of the experiment}
    \label{timeline}
    \begin{center}
        \centering
        \includegraphics[width=0.70\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{timeline\_suc\_exp.do}}
\end{figure}

\begin{figure}[H]
        \caption{Experiment arms}
    \label{exp_arms}
    \begin{center}
        \centering
        \includegraphics[width=0.70\textwidth]{Figuras/exp_arms.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ }
\end{figure}

@@

\begin{figure}[H]
    \caption{Treatment Effect}
    \label{Treatment Effect}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Paid loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_des_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_num_p.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Percentage of payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_sum_porcp_c.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Refrendum}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_ref_c.pdf}
    \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
      \caption{Days to un-pledge}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_dias_al_desempenyo.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
\end{figure}

\begin{figure}[H]
        \caption{Reincidence}
    \label{reincidence_welfare}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_reincidence.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ }
\end{figure}

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect}
    \label{heterogeneous_te}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Paid loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_num_p.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Percentage of payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_sum_porcp_c.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Refrendum}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_ref_c.pdf}
    \end{subfigure}    
    \begin{subfigure}{0.4\textwidth}
      \caption{Days to un-pledge}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_dias_al_desempenyo.pdf}
    \end{subfigure}    
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf.do}}
\end{figure}

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect for Paid Loan}
    \label{heterogeneous_paid_loan}
    \begin{center}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_3.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_3.pdf}
    \end{subfigure}
     \begin{subfigure}{0.3\textwidth}
      \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
      \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_dist_des_c_pro_5.pdf}
    \end{subfigure} 
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_5.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf.do}}
\end{figure}

@@

\begin{table}[H]
\caption{Treatment effects results (conditional on positive payment)}
\label{te_robust_table}
\begin{center}
\scriptsize{\input{./Tables/te_robust.tex}}
\end{center}
 \footnotesize
\textit{Notes:}

@@

\begin{figure}[H]
    \caption{Robustness check effect of arms in reincidence}
    \label{robust_reincidence}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
        \caption{ No Choice/Fee}
        \centering
        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p2.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
      \caption*{No Choice/No fee}
        \centering
        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p3.pdf}
    \end{subfigure}

@@

\begin{figure}[H]
    \caption{Treatment Effect (conditional to positive payment)}
    \label{te_robust_table}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Paid loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_des_c_robust.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_num_p_robust.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Percentage of payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_sum_porcp_c_robust.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Referendum}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_ref_c_robust.pdf}
    \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
      \caption{Days to un-pledge}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_dias_al_desempenyo_robust.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
\end{figure}

\begin{figure}[H]
        \caption{Reincidence (conditional to positive payment)}
    \label{reincidence_positive}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_reincidence_robust.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ }
\end{figure}
